---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
unzip('activity.zip')
activityData <- read.csv(file="activity.csv")
```


## What is mean total number of steps taken per day?
### Make a histogram of the total number of steps taken each day
```{r}
stepsData<- aggregate(steps ~ date, data = activityData, FUN=sum)
barplot(stepsData$steps, names.arg=stepsData$date, ylab='No. of Steps',las=2)
```

### Calculate and report the mean and median total number of steps taken per day

The mean number of steps taken per days is:
```{r}
mean(stepsData$steps)
```

The median number of steps taken per days is:
```{r}
median(stepsData$steps)
```

## What is the average daily activity pattern?

### Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis)
### and the average number of steps taken, averaged across all days (y-axis)

```{r}
stepsData.interval <- aggregate(steps ~ interval, data = activityData, FUN=mean)
plot(stepsData.interval,type="l")
```

### Which 5-minute interval, on average across all the days in the dataset,
### contains the maximum number of steps?

```{r}
stepsData.interval$interval[which.max(stepsData.interval$steps)]
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
